Flabby and injective objects in toposes

### 2024-01-11 paper-flabby-objects.tex
to do
regen pdf
typo

Trivially, every group satisfying the Baer condition is also divisible.

@@

\begin{proof}For the first part, an abelian group~$A$ embeds into the
divisible group~$\QQ\langle A \rangle / K$, where~$\QQ\langle A \rangle$ is the
underlying abelian group of the free~$\QQ$-vector space on~$A$ and~$K$ is the
kernel of the canonical map~$\ZZ\langle A \rangle \to A$.

@@

>>>>

Every group satisfying the Baer condition is divisible, by specializing~$\aaa$
to the ideal~$(n)$ and using multiplication by~$x$ as the map~$\aaa \to I$.

@@

\begin{proof}For the first part, an abelian group~$A$ embeds into the
divisible group~$\QQ\langle A \rangle / K$, where~$\QQ\langle A \rangle$ is the
underlying abelian group of the free~$\QQ$-vector space on the underlying set of~$A$ and~$K$ is the
kernel of the canonical map~$\ZZ\langle A \rangle \to A$.

@@

https://arxiv.org/abs/1903.01211
